### 2024-03-19 manuscript.Rmd
Add documentation to code

```{r positive_life_event}
plot_single_person(5, 0.2)
```

@@

```{r negative_life_event}
plot_single_person(5, -0.2)
```

>>>>

```{r positive_life_event}
person <- list(
  emotional_reactivity = 0.5,
  adaptation_rate = 0.5,
  SWB_set_point = 0.5
)

plot_single_person(person, 5, 0.2)
```

@@

```{r negative_life_event}
person <- list(
  emotional_reactivity = 0.5,
  adaptation_rate = 0.5,
  SWB_set_point = 0.5
)

plot_single_person(person, 5, -0.2)
```
